Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
Review axevent

\subsubsection{axptz}
%Add info about this is one of the added changes
The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.

@@

%%Real category
Given this information, we concluded that we were correct in predicting that this change was enhancive. The prediction of the secondary category was also correct.

@@

%%Describe the change 
Version 2.0 of the API has been designed around an event driven system, as such, it's not surprising that the old event system had to be re-implemented. The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera. This event system is combined with the use of callbacks to create a robust event driven API.

%%Relate it to Categories
Given that this feature was a re-implementation, we concluded that it should be classified mainly as an enhancive change with the subcategory of change being classified as groomative. Groomative was chosen as a subcategory due to the alternate intention of bringing the new feature in line with the new interface.

The interviewee mentioned that the previous version of axevent, event, was being deprecated in favour of this new implementation. The primary reason was to bring the implementation into line with the new way that the API handles events and interfaces as a whole. The interviewee mentioned that they realised that the API was hard to use previously and that improving it this way, through the use of re-implementations, could allow them to create an easier to use API.

Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory. This is the reverse of what we concluded and as such means that we incorrectly determined the intent for this change.

>>>>

\subsubsection{axptz}
%Add info about this is one of the added changes XXX (do that for all)
The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.

@@

%%Category based on her information
Given this information, we concluded that we were correct in predicting that this change was enhancive. The prediction of the secondary category was also correct.

@@

%%Describe the change 
Version 2.0 of the API was designed to be event-driven system which makes use of callbacks. To achieve this, the old event system had to be re-designed. The new event system is used by all features of version 2.0. An example of when an event is generated is when movement is detected by the camera.

%%Relate it to Categories
Given that this module was a re-implementation previous event system, we concluded that it should be classified mainly as an enhancive change with the secondary category being classified as groomative. Groomative was chosen as the secondary category due to the additional motive of bringing the new feature in line with the new interface.

%%What she said 
%%Re-write this... the main reason was functioanlity and not usability stuff XXX
The interviewee outlined that the previous version of axevent, event, was deprecated in favour. The primary reason for this was to bring the implementation into line with the new design of the event system and interfaces. The interviewee expressed that they were unsatisfied with certain usability aspects of the API.

%%Category based on her information
Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory. This is the reverse of what we concluded and as such means that we incorrectly determined the intent for this change.
